---
title: "HW 4"
author: "Kate Spiekerman, kls5665"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r global_options, echo=FALSE}
knitr::opts_chunk$set(fig.height=4, fig.width=5, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=60))
```

```{r, echo=FALSE, message=FALSE}
gas <- read.csv('gasprices.csv')

library(tidyverse)
library(ggplot2)
library(mosaic)
```


## **Question 1**

**Theory A**

Claim- Gas stations charge more if they lack direct competition in sight

```{r, echo=FALSE}
competition <- gas %>%
  filter(Competitors == 'Y')
no_competition <- gas%>%
  filter(Competitors == 'N')

boxplot(gas$Price~gas$Competitors, main='Distribution of Gas Prices',ylab='Price',xlab='Competition',names=c('No','Yes'), col=c('#a8ddb5','#43a2ca'))

boot_comp <- do(10000)*mean(~Price, data=mosaic::resample(competition))
boot_comp %>%
  summarise(standard_error = sd(mean))

confint(boot_comp, level = .95)

boot_no_comp <- do(10000)*mean(~Price, data=mosaic::resample(no_competition))
boot_no_comp %>%
  summarise(standard_error = sd(mean))

confint(boot_no_comp, level = .95)

```
Evidence- The confidence interval for the gas stations with competition was (1.8326, 1.873) and the confidence interval for the gas stations with no competition was (1.8527, 1.8996). 

Conclusion- Based on the data, I would not agree with the theory that gas stations without competition charge more than those with it.


**Theory B**

Claim- The richer the area, the higher the gas prices.

```{r, echo=FALSE}
ggplot(gas) + 
  geom_point(aes(x=Income, y=Price))

cor(gas$Income, gas$Price)

```

Evidence- There is a slight positive linear correlation between richer areas and higher gas prices. 

Conclusion- Based on the data, I would agree with the theory that richer areas have higher gas prices. 


**Theory C**

Claim- Gas stations at stoplights charge more.

```{r, echo=FALSE}
stoplight <- gas %>%
  filter(Stoplight == 'Y')
no_stoplight <- gas%>%
  filter(Stoplight == 'N')

boxplot(gas$Price~gas$Stoplight, main='Distribution of Gas Prices',ylab='Price',xlab='Stoplights',names=c('No','Yes'), col=c('#a8ddb5','#43a2ca'))

boot_light <- do(10000)*mean(~Price, data=mosaic::resample(stoplight))
boot_light %>%
  summarise(standard_error = sd(mean))

confint(boot_light, level = .95)

boot_no_light <- do(10000)*mean(~Price, data=mosaic::resample(no_stoplight))
boot_no_light %>%
  summarise(standard_error = sd(mean))

confint(boot_no_light, level = .95)

```
Evidence- The confidence interval for the gas stations with competition was (1.8446, 1.8817) and the confidence interval for the gas stations with no competition was (1.8387, 1.8963).

Conclusion- Based on the data, I would not agree with the theory that gas stations near a stoplight charge more than those not near a stoplight. 


**Theory D**

Claim- Gas stations with direct highway access charge more

```{r, echo=FALSE}
highway <- gas %>%
  filter(Highway == 'Y')
no_highway <- gas%>%
  filter(Highway == 'N')

boxplot(gas$Price~gas$Highway, main='Distribution of Gas Prices',ylab='Price',xlab='Highway',names=c('No','Yes'), col=c('#a8ddb5','#43a2ca'))

boot_highway <- do(10000)*mean(~Price, data=mosaic::resample(highway))
boot_highway %>%
  summarise(standard_error = sd(mean))

confint(boot_highway, level = .95)

boot_no_highway <- do(10000)*mean(~Price, data=mosaic::resample(no_highway))
boot_no_highway %>%
  summarise(standard_error = sd(mean))

confint(boot_no_highway, level = .95)

```
Evidence- The confidence interval for the gas stations near a highway was (1.8695, 1.9304) and the confidence interval for the gas stations with no competition was (1.8367, 1.8724).

Conclusion- Based on the data, I would agree with the theory that gas stations near a highway charge more than those not near a highway.


**Theory E**

Claim- Shell charges more than all other non-Shell brands.

```{r, echo=FALSE}
shell <- gas %>%
  filter(Brand == 'Shell')
no_shell <- gas%>%
  filter(Brand != 'Shell')

boxplot(gas$Price~gas$Brand, main='Distribution of Gas Prices',ylab='Price',xlab='Brand')

boot_shell <- do(10000)*mean(~Price, data=mosaic::resample(shell))
boot_shell %>%
  summarise(standard_error = sd(mean))

confint(boot_shell, level = .95)

boot_no_shell <- do(10000)*mean(~Price, data=mosaic::resample(no_shell))
boot_no_shell %>%
  summarise(standard_error = sd(mean))

confint(boot_no_shell, level = .95)
```
Evidence- The confidence interval for the gas stations with competition was (1.8517, 1.9166) and the confidence interval for the gas stations with no competition was (1.8391, 1.8741).

Conclusion- Based on the data, I would not agree with the theory that shell gas stations charge more than non shell gas station. 


## **Problem 2**

**Part A**

```{r}
cars <- read.csv('sclass.csv')

car_1 <- cars%>%
  filter(year == 2011 & trim == "63 AMG")

boxplot(car_1$mileage, main='Distribution of Gas Prices',ylab='Price')

boot_car_1 <- do(10000)*mean(~mileage, data=mosaic::resample(car_1))
boot_car_1 %>%
  summarise(standard_error = sd(mean))

confint(boot_car_1, level = .95)


```
The confidence interval for cars made in 2011 and 63 AMG trim was (26211.28, 31785.95), with the point estimate being 29339.07.  



**Part B**

```{r}
car_2 <- mutate(cars, isBlack = ifelse(color == 'Black', TRUE, FALSE))
car_black <- filter(car_2, year == 2014 & trim == '550')



```

The confidence interval for cars made in 2014 and 550 trim was . 


## **Problem 3**

```{r}
nbc <- read.csv('nbc_pilotsurvey.csv')

```

**Part A**

Question- Which show has a higher happy rating, Living with Ed or My Name is Earl?

Approach- Take a bootstrap sample of each and compare them. 

```{r}
ed <- nbc%>%
  filter(Show == "Living with Ed" )
         
earl <- nbc%>%
  filter(Show == "My Name is Earl")

boot_earl <- do(10000)*mean(~Q1_Happy, data=mosaic::resample(earl))
boot_earl %>%
  summarise(standard_error = sd(mean))

confint(boot_earl, level = .95)

boot_ed <- do(10000)*mean(~Q1_Happy, data=mosaic::resample(ed))
boot_ed %>%
  summarise(standard_error = sd(mean))

confint(boot_ed, level = .95)
```

Results- The confidence interval for happiness for Living with Ed was (3.7106, 3.9489) and the confidence interval for My Name is Earl was (3.7195, 4.1341).

Conclusion- In conclusion, the intervals happiness rating for Living with Ed is slightly lower than the happiness rating for My Name is Earl. 

**Part B**

Question- Which show has a higher annoyed rating, The Biggest Loser or The Apprentice: Los Angeles? 

Approach- Take a bootstrap sample of each and compare them.

```{r}
loser <- nbc%>%
  filter(Show == "The Biggest Loser")

la <- nbc%>%
  filter(Show == "The Apprentice: Los Angeles")

boot_loser <- do(10000)*mean(~Q1_Annoyed, data=mosaic::resample(loser))
boot_loser %>%
  summarise(standard_error = sd(mean))

confint(boot_loser, level = .95)

boot_la <- do(10000)*mean(~Q1_Annoyed, data=mosaic::resample(la))
boot_la %>%
  summarise(standard_error = sd(mean))

confint(boot_la, level = .95)
```

Results- The confidence interval for annoyed for The Biggest Loser was (1.8623, 2.2174) and the confidence interval for The Apprentice: Los Angeles was (3.7195, 4.1341). 

Conclusion- In conclusion, the intervals for annoyed rating for The Biggest Loser is significantly lower than the annoyed rating for The Apprentice: Los Angeles. 

**Part C**

Question- What proportion of viewers find the show, Dancing with the Stars, confusing to understand. 

Approach- Take a proportion bootstrap of the proportion of viewers who thought the show was confusing. 

```{r}
dancing <- nbc%>%
  filter(Show == "Dancing with the Stars")

```

Results- 

Conclusion-


## **Problem 4**

```{r, echo=FALSE, results= 'hide'}
ebay <- read.csv('ebay.csv')

ebay_2 <- ebay%>%
  mutate(Ratio = rev_after/rev_before)

boot_ebay = do(10000) * diffmean(Ratio ~ adwords_pause, data = mosaic::resample(ebay_2))
confint(boot_ebay, level = .95)

```

Question- What is the difference between the ratios of the treatment and control group.

Approach- I added a column, ratio, to the data set. Then I bootstrapped the average difference in the average ratios for the control and the treatment group. 

Results- With the 95% confidence interval, the difference between the two means is between -.091 and -.013.

Conclusion- The interval does not contain zero so it is considered statistically significant. 





